\documentclass[margin, 10pt]{res}

\usepackage{helvet} 

\setlength{\textwidth}{5.1in} 

\begin{document}


\moveleft.5\hoffset\centerline{\large\bf Ashwini Mohan}
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip 
 
\moveleft.5\hoffset\centerline{#44/3 5th main,1st Stage}
\moveleft.5\hoffset\centerline{RK layout, Padmanabhanagar, Bangalore-70}
\moveleft.5\hoffset\centerline{mohanashwini96@gmail.com,9972009473

\begin{resume}
\section{OBJECTIVE}  

To succeed in an environment of growth and excellence to earn a job which provides me job satisfaction and self-development help me achieve personal as well as organization growth.

\section{EDUCATION}

{\sl Bachelor of Engineering, Information Technology,} Global Academy of Technology, Bangalore \\
{\sl PU, PCME, } Sri Kumaran Children's Home PU College, Bangalore \\
{\sl School, } Carmel school, Bangalore\\

\section{TECHNICAL\\ SKILLS} 

{\sl  Operating Systems:} 
Windows, Mac OSX \\
Core java \\
SQL \\
HTML, CSS, JAVASCRIPT \\
C, C++ \\
 
\section{INTERPERSONAL SKILLS} \\
\begin{itemize} \itemsep -2pt 
\item Good Communication skills and analysis.
\item Written and verbal communication skills.
\item Worked well as a part of a team in various event organizations.
\item Leadership qualities and ability to take initiative.
\end{itemize}
 
\section{PROJECTS} \\
{\sl TITLE:}
Face detection and Recognition for automated attendance system.
Tools used are Open CV and Python. \\
{\sl TOOLS:}
Open CV, Python. \\
{\sl DESCRIPTION:}
Automated Attendance Management System performs daily activites of attendance marking and analysis with reduced human intervensions. This is done by detecting and recognizing the facial features of the student and updating student's attendance in the database. \\


\section{COMMUNITY \\ SERVICE}

Worked as a part of YOUTH FOR PARIVARTHAN drives conducted at various parts of bangalore

\section{EXTRA-CURRICULAR \\ ACTIVITIES} \\
\begin{itemize} \itemsep -2pt
\item Junior in classical music.
\item Junior in classical dance.
\item Poster Presentation about Google products entitled with G PRODUCTS
\item Participated in Open Day Project Exhibition at GSSSIT Mysore, April 2018.
\item Participated in Open Day Project Exhibition at DSAT Bangalore, April 2018.
\end{itemize}

\section{DECLARATION} \\
I hereby declare that the information provided is true to the best of my knowledge.

\end{resume}
\end{document}
